---
title: "Quantitative assignment"
author: "Gayoung Park"
output: html_document
bibliography:
  - quan.bib
---



```{r setup, echo=FALSE, results='hide' }
# install.packages(pkgs = "devtools", dependencies = TRUE)
knitr::opts_chunk$set(message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE)
```

```{r, echo=FALSE, results='hide'}
library(devtools)
#install_github("benmarwick/JSTORr")
```

```{r, echo=FALSE, results='hide'}
library("JSTORr")
library(dplyr)
multiple_archives <- JSTOR_unpack_multiple_archives(mydir = "~/scientifcexplantion/data/one_gram")
save(multiple_archives, file="~/scientifcexplantion/data/one_gram/multiple_archives.RData")
load("data/one_gram/multiple_archives.RData")
```

##Introduction
The main purpose of this paper is to find the relationship between several keywords which are related with my research questions by exploring sets of archaeological keys words in corpus based on archaeological journals. I expect that the results of this project will provide background knowledge about my topics and tendency of relating studies. 

##Hypothesis to test

Three potential questions are related with my research subject that is about stemmed points in Upper Paleolithic Korean peninsula and main focus of the subject is to figure out the driver(s) that let people produce the lithics and the cause(s) of the changes in stemmed points throughout the Upper Paleolithic in Korea. My hypothesis is that possible causes of producing stemmed points might be interpreted with evolutionary theory, extinction theory, and climate change. For example, due to climate change, the main food resources such as animals and plants were extinct so hunter-gatherers tried to survive adapting the new environmental with using new tools in the mechanism of evolutionary theory. 

Based on my hypothesis, I make three questions:
(1) Is there some relationship between the extinction of mammals such as mammoth and change of stone tool? If so, I would like to see the transition between phase to phase of stemmed point based on the theory of the extinction.
(2) How can I connect the theory of evolution and the starting point of new lithics such as stemmed point in the Upper Paleolithic period?
(3) Which attributes on lithics I should choose to figure out changing aspect of lithic according to climate change?

##Key terms
The keywords for this project are **lithic**, **extinction**, **evolution**, **climate**. I think these four words are apparently the most important key terms in my research questions to explore data collection. Through three different combinations of **lithic** and other keywords, I hope that I can find a certain clue of my further research.  

##Exploratory Data Analysis
Provided data collection, or corpus, is consisted of five journals: American Antiquity, Journal of Archaeological Research, World Archaeology, Journal of World Prehistory, and Journal of Field Archaeology. The mechanism of this project is quite simple statistic. I used specific functions which show frequency of use of the one word and two words in corpus and visualize the result with plot. They also show the relationship between two words by showing the frequency of use in articles.


1.  Lithic and extinction
To approach the first question, the relationship between the theory of extinction and its impact on lithics, I analyze the frequency of words, lithic and extinction. Figure 1 illustrates the frequency of extinction in the corpus from 1930’s to 2012. Extinction has become common word in archaeology but the frequency per 1000 words is decreasing. The word lithic is also popular but it keeps being used in high frequency per 1000 words (Figure 2). Especially after 70’s the number of use of the two words are highly increasing, I think it follows the growth of archaeological research. According to Figure 3, the degree of correlation between the two words seems not high. The size of dot indicates the strength of the relationship for all articles per year. I can see relatively bigger dot in 2006, but it still indicates only 0.5 point which is not a strong relationship. At least, the point, higher than 1.0, can be regarded as a strong relationship. Figure 4 shows associated words relating extinction used in article. I divide the period from 1988 to 2012 per 5 years. Among them, from 1998 to 2002, the word Pleistocene was used over 900 times with extinction. Besides, shell, population, stone, Paleolithic were used frequently. Like figure4, figure 5 indicates associated words relating not just extinction but both lithic and extinction. From 1975 to 2008, the frequency of the words increased, the word settlement was used over 3000, stone, point, population were used frequently. Except less-meaningful words such as number or field, the result is quite useful to my research question, the theory of extinction and its impact on lithics. Especially, if one of frequent word, point means projectile point, then the result would perfectly match with my expectation. To test my hypothesis, I search the most correlated article for word extinction in my journal data using specific function. The article is as following: Jim J. Hester, 1960, Late Pleistoncene Extinction and Radiocarbon Dating, American Antiquity, 26, 1:58-77. In this article, the author points out errors in existing knowledge of extinct period of last Pleistocene mammals in North America and he corrects the sequence based on radio carbon dated. Even though his main point is dating and sequence of extinction of American mammal, I can find the relationship between the extinction of mammals and lithics, especially, points. He mentions Clovis points, Lerma points, and flake point with extinction [@hester_late_1960]. Therefore I can expect that there was correlation between the extinction of mammals and its impact on lithics, points, in Upper Paleolithic period. And my research question is worth to look into it. 


```{r}
#Figure 1
# one words
extinction <- JSTOR_1word(multiple_archives, "extinction")
extinction$plot
extinction_tbl <- extinction$word_by_year
extinction_tbl[which.max(extinction_tbl$word_ratio),]
#searching article url:http://www.jstor.org/stable/last6digits  
#[@Hester_1960]
```
Figure 1. Frequency of extinction 

```{r}
#Figure 2
# two words
ex_lithic <- JSTOR_2words(multiple_archives, "extinction", "lithic")
ex_lithic$plot 
```
Figure 2. Frequency of extinction and lithic

```{r}
#Figure 3
# correlation of two words
co_ex_lithic <- JSTOR_2wordcor(multiple_archives, "extinction", "lithic")
co_ex_lithic$plot

```
Figure 3. Correlation of extinction and lithic

```{r}
#create a document term matrix of nouns only
nouns <- JSTOR_dtmofnouns(multiple_archives, sparse = 1, POStag = FALSE)

#delete common archaeological words
custom_stopwords <- c('archaeology', 'university', 'research', 'evidence', 'journal', 'world', 'site', 'cambridge', 'archaeol', 'area', 'region', 'period', 'analysis', 'anthropology', 'springer', 'production', 'figure', 'work', 'world', 'concept', 'human', 'middle', 'altamira', 'culture', 'record', 'citation', 'discipline', 'author', 'proportion', 'literature', 'report', 'approach', 'cambridge' )
```

```{r, echo=FALSE, results='hide'}

extinction_nouns <- JSTOR_dtmofnouns(multiple_archives, word = "extinction", sparse = 1, POStag = TRUE)
#Figure 4
extinction_freqwords <- JSTOR_freqwords(multiple_archives, extinction_nouns, custom_stopwords, n = 5)
```
Figure 4. Words relating extinction

```{r, echo=FALSE, results='hide'}
ex_lithic_nouns <- JSTOR_dtmofnouns(multiple_archives, word = c("extinction","lithic"), sparse = 1, POStag = TRUE)
#Figure 5
ex_lithic_freqwords <- JSTOR_freqwords(multiple_archives, ex_lithic_nouns, custom_stopwords, n = 5)
```
Figure 5. Words relating extinction and lithic

2.  Lithic and evolution
Like former set, the words lithic and evolution are selected to explore in my corpus. My research question is to figure out the relationship between human evolution and its impact on lithics in Upper Paleolithic. I expect the result will show that evolution to modern human would cause certain change in lithic assemblages. Figure 6 illustrates the frequency of use of word evolution in archaeological articles. After 70’s the evolution became common and popular word. As I mentioned in the former chapter, the the word lithic also became popular at the same time. Figure 7 is covered with a lot of dots after 70’s. However, the strongest correlation of the two words can be seen in 1953 (Figure 8). Even though the value is not higher than 1.0, but the the tendency is quite interesting. Usage of the two words gets increasing while their relationship of both words is decreasing. Figure 9 shows associated words with evolution. From 1994 to 2008, the word settlement was used the most frequently, more than 3000 times. Population, stone, are pottery were also used frequently. Figure 10 indicates that the words number and settlement were strongly associated words with both evolution and lithic from 1980 to 2009. The words surface, stone, population and point were also frequently used with the two key words within articles. But it is hard to infer the meaning of “number” and why “number” was frequently used. Unlike my expectation or recognition of evolution as evolution of hominine, there are no Homo sapiens, modern human, or Pleistocene. Using specific function, I find the most related article with the word evolution, Robert C. Dunnell and Robert J. Wenke, 1980, Cultural and Scientific Evolution: Some Comments on “The Decline and Rise of Mesopotamian Civilization”, American Antiquity, 45, 3:605-609. The article is review of Norman Yoffee’s article which is a about the understanding of the development and history of complex societies in the frame of evolutionary theory. This article is based on cultural evolution and the second millennium B.C. in Mesopotamia which is not relevant with my research question [@dunnell_cultural_1980]. I expected to find an article which is about genetic evolution and Paleolithic period but there is no mention about genetic, lithic or stone tool, or even animals. Therefore my second set of key words is not appropriate to the quantitative research. 


```{r}
#Figure 6
# one words
evolution <- JSTOR_1word(multiple_archives, "evolution")
evolution$plot
evolution_tbl <- evolution$word_by_year
evolution_tbl[which.max(evolution_tbl$word_ratio),]
#[@Dunnell and Dunnell_1960]
```
Figure 6. Frequency of evolution 

```{r}
#Figure 7
# two words
ev_lithic <- JSTOR_2words(multiple_archives, "evolution", "lithic")
ev_lithic$plot
```
Figure 7. Frequency of evolution and lithic

```{r}
#Figure 8
# correlation of two words
co_ev_lithic <- JSTOR_2wordcor(multiple_archives, "evolution", "lithic")
co_ev_lithic$plot
```
Figure 8. Correlation of evolution and lithic

```{r, echo=FALSE, results='hide'}
evolution_nouns <- JSTOR_dtmofnouns(multiple_archives, word = "evolution", sparse = 1, POStag = TRUE)
#Figure 9
evolution_freqwords <- JSTOR_freqwords(multiple_archives, evolution_nouns, custom_stopwords, n = 5)
```
Figure 9. Words relating evolution

```{r,echo=FALSE, results='hide'}
ev_lithic_nouns <- JSTOR_dtmofnouns(multiple_archives, word = c("evolution","lithic"), sparse = 1, POStag = TRUE)
#Figure 10
ev_lithic_freqwords <- JSTOR_freqwords(multiple_archives, ev_lithic_nouns, custom_stopwords, n = 5)
```
Figure 10. Words relating evolution and lithic

3.  Lithic and climate
Third set of key words is lithic and climate. Through these key words, I would like to find the relationship between climate change and its impact on lithic. Figure 11 indicates the frequency of use the word climate in archaeological articles. Climate has been used from 1934 and popular from beginning. Figure 12 shows how these two key words are common and popular in archaeology. Also the two words are strongly related with each other. In figure 13, the correlation is confirmed. The strongest correlation was in 1939. And many dots indicating positive value are can be seen in this plot. I can infer that climate change has been frequently dealt with prehistory and lithics in archaeology. The associated words with climate are similar with evolution (Figure 14). From 1983 to 2012, the more frequent word is settlement. Based on my mechanism which is climate change can impact on human’s settlement strategy so they should try new thing to adjust severe environment such as producing new lithics, projectile points. The words population, stone, and Pleistocene were also used frequently. Figure 15 shows associated words with climate and lithic. The words settlement and number have been frequently used more than 4,000 times. Similar with the case of the set of evolution and lithic, the meaning of number is not clear. As I expected, the words stone, population, and point can be seen in the plot. I search the most related article with the word climate which is as following: David J. Meltzer and Vance T. Holiday, 2010, Would North American Paleoindians have Noticed Younger Dryas Age Climate Changes?, Journal of World Prehistory, 23, 1:1-41. In this article, the authors mention Paleoindian groups in North America during Younger Dryas Chronozone. Even though they do not agree with, but there is a strong mechanism about climate which is exactly same with mine. Low temperature during Younger Dryas impacted on biotic communities surrounding human and it became challenge to adapt the environment for human. The authors’ response about the mechanism is that Younger Dryas on the Great Plains and in Rocky Mountain was not extremely cold and human could successfully disperse across everywhere in North America. And the authors say it is hard to demonstrate the direct relationship between particular climate change recorded in archaeological data and change in artifacts. “Linking climate and culture change requires both tight chronological correlation and (more) strong evidence of causation” (P.30) [@meltzer_would_2010]. I agree with the authors of the article. It is hard to find strong and direct relationship between the climate and change of lithics. The results of this project say that I have to specify my research question.  


```{r}
#Figure 11
# one words
climate <- JSTOR_1word(multiple_archives, "climate")
climate$plot
climate_tbl <- climate$word_by_year
climate_tbl[which.max(climate_tbl$word_ratio),]
#[@Meltzer and Holliday_2010]
```
Figure 11. Frequency of climate 

```{r}
#Figure 12
# two words
cl_lithic <- JSTOR_2words(multiple_archives, "climate", "lithic")
cl_lithic$plot
```
Figure 12. Frequency of climate and lithic

```{r}
#Figure 13
# correlation of two words
co_cl_lithic <- JSTOR_2wordcor(multiple_archives, "climate", "lithic")
co_cl_lithic$plot
```
Figure 13. Correlation of climate and lithic

```{r,echo=FALSE, results='hide'}
climate_nouns <- JSTOR_dtmofnouns(multiple_archives, word = "climate", sparse = 1, POStag = TRUE)

#Figure 14
climate_freqwords <- JSTOR_freqwords(multiple_archives, climate_nouns, custom_stopwords, n = 5)
```
Figure 14. Words relating climate

```{r,echo=FALSE, results='hide'}
cl_lithic_nouns <- JSTOR_dtmofnouns(multiple_archives, word = c("climate","lithic"), sparse = 1, POStag = TRUE)

cl_lithic_freqwords <- JSTOR_freqwords(multiple_archives, cl_lithic_nouns, custom_stopwords, n = 5)
```
Figure 15. Words relating climate and lithic


##Discussion and Conclusion

Through this project, quantitative research, I could test whether my research questions are reasonable or not by getting frequency of key words in archaeological journals with statistical coding functions. My hypothesis drivers of introduction of new lithics, stemmed points in Upper Paleolithic might be related with evolution, extinction, and climate change. On the basis of the hypothesis, I make three research questions which ask (1) relationship between the extinction of mammals and change of stone tool (2) connection of evolution and the introduction of new lithics and (3) impact of climate on lithics. My key words to explore data base are **lithic**, **extinction**, **evolution**, **climate**. 

Using several functions, I could derive the results of frequency, correlation, and associated words of the key words. The results say that my first question is reasonable to continue to analyze. It has right direction, at least using key words. However, the second set of keywords show unexpected results. I regarded evolution as genetic evolution to modern human but the results indicate cultural evolution and show unrelated words. For this reason, I should change my second research question or adjust it to be more reasonable. The results of third set say that the direction of my research question is reasonable but it is hard to demonstrate in archaeological data. To develop the question, I should consider the method to verify the relationship in archaeological record.  

In conclusion, to build a model or develop a hypothesis, testing a few relating key words statistically could mark a milestone in the entire process of research. It can give a background knowledge as well as present right direction of research. But it also has limitations. Depending on the kinds of Journals and the number of ones in data base, the results can be different. Also, due to use of different terms for one notion, the result could be contaminated. However, mostly, the problems are related with technology such as problem in coding or one in computer. Therefore, if this method become popular and technology would develop following the popularity, then most of limitation would be solved. 

##Reference

