---
title: "Quantitative assignment"
author: "Gayoung Park"
date: "June 4th, 2015"
bibliography:
  - quan.bib
output: rmarkdown::tufte_handout
---

```{r setup, echo=FALSE}
# install.packages(pkgs = "devtools", dependencies = TRUE)
knitr::opts_chunk$set(message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE)
```

##Introduction
The main purpose of this paper is to find the relationship between several keywords which are related with my research questions by exploring sets of archaeological keys words in corpus based on archaeological journals. I expect that the results of this project will provide background knowledge about my topics and tendency of relating studies. 

##Hypothesis to test

Three potential questions are related with my research subject that is about stemmed points in Upper Paleolithic Korean peninsula and main focus of the subject is to figure out the driver(s) that let people produce the lithics and the cause(s) of the changes in stemmed points throughout the Upper Paleolithic in Korea. My hypothesis is that possible causes of producing stemmed points might be interpreted with evolutionary theory, extinction theory, and climate change. For example, due to climate change, the main food resources such as animals and plants were extinct so hunter-gatherers tried to survive adapting the new environmental with using new tools in the mechanism of evolutionary theory. 

Based on my hypothesis, I make three questions:
(1) How can I connect the theory of evolution and the starting point of new lithics such as stemmed point in the Upper Paleolithic period?
(2) Is there some relationship between the extinction of mammals such as mammoth and change of stone tool? If so, I would like to see the transition between phase to phase of stemmed point based on the theory of the extinction.
(3) Which attributes on lithics I should choose to figure out changing aspect of lithic according to climate change?

##Key terms
The keywords for this project are **lithic**, **extinction**, evolution**, **climate**. I think these four words are apparently the most important key terms in my research questions to explore data collection. Through three different combinations of **lithic** and other keywords, I hope that I can find a certain clue of my further research.  


```{r}
library(devtools)
#install_github("benmarwick/JSTORr")
```


```{r}
library("JSTORr")
library(dplyr)
#multiple_archives <- JSTOR_unpack_multiple_archives(mydir = "~/scientifcexplantion/data/one_gram")
#save(multiple_archives, file="~/scientifcexplantion/data/one_gram/multiple_archives.RData")
load("data/one_gram/multiple_archives.RData")
```


#extinction, extinction&lithic

```{r}
#Figure 1
# one words
extinction <- JSTOR_1word(multiple_archives, "extinction")
extinction$plot
extinction_tbl <- extinction$word_by_year
extinction_tbl[which.max(extinction_tbl$word_ratio),]
#searching article url:http://www.jstor.org/stable/last6digits  
#[@Hester_1960]
```

```{r}
#Figure 2
# two words
ex_lithic <- JSTOR_2words(multiple_archives, "extinction", "lithic")
ex_lithic$plot
```

```{r}
#Figure 3
# correlation of two words
co_ex_lithic <- JSTOR_2wordcor(multiple_archives, "extinction", "lithic")
co_ex_lithic$plot
```

```{r}
#Figure 4
nouns <- JSTOR_dtmofnouns(multiple_archives, sparse = 1, POStag = FALSE)
PCA_extinction <- JSTOR_clusterbywords(nouns, "extinction", f = 0.005)
```

```{r}
#delete common archaeological words
custom_stopwords <- c('archaeology', 'university', 'research', 'evidence', 'journal', 'world', 'site', 'cambridge', 'archaeol', 'area', 'region', 'period', 'analysis', 'anthropology', 'springer', 'production', 'figure', 'work', 'world', 'concept', 'human', 'middle', 'altamira', 'culture', 'record', 'citation', 'discipline', 'author', 'proportion', 'literature', 'report', 'approach', 'cambridge' )
```

```{r}
#Figure 5
extinction_nouns <- JSTOR_dtmofnouns(multiple_archives, word = "extinction", sparse = 1, POStag = TRUE)
extinction_freqwords <- JSTOR_freqwords(multiple_archives, extinction_nouns, custom_stopwords, n = 5)
```

```{r}
#Figure 6
ex_lithic_nouns <- JSTOR_dtmofnouns(multiple_archives, word = c("extinction","lithic"), sparse = 1, POStag = TRUE)
ex_lithic_freqwords <- JSTOR_freqwords(multiple_archives, ex_lithic_nouns, custom_stopwords, n = 5)
```


#evolution, evolution&lithic


```{r}
# one words
evolution <- JSTOR_1word(multiple_archives, "evolution")
evolution$plot
evolution_tbl <- evolution$word_by_year
evolution_tbl[which.max(evolution_tbl$word_ratio),]
#[@Dunnell and Dunnell_1960]
```

```{r}
# two words
ev_lithic <- JSTOR_2words(multiple_archives, "evolution", "lithic")
ev_lithic$plot
```

```{r}
# correlation of two words
co_ev_lithic <- JSTOR_2wordcor(multiple_archives, "evolution", "lithic")
co_ev_lithic$plot
```

```{r}
PCA_evolution <- JSTOR_clusterbywords(nouns, "evolution", f = 0.005)
```

```{r}
evolution_nouns <- JSTOR_dtmofnouns(multiple_archives, word = "evolution", sparse = 1, POStag = TRUE)
evolution_freqwords <- JSTOR_freqwords(multiple_archives, evolution_nouns, custom_stopwords, n = 5)
```

```{r}
ev_lithic_nouns <- JSTOR_dtmofnouns(multiple_archives, word = c("evolution","lithic"), sparse = 1, POStag = TRUE)
ev_lithic_freqwords <- JSTOR_freqwords(multiple_archives, ev_lithic_nouns, custom_stopwords, n = 5)

```


#climate, climate&lithic

```{r}
# one words
climate <- JSTOR_1word(multiple_archives, "climate")
climate$plot
climate_tbl <- climate$word_by_year
climate_tbl[which.max(climate_tbl$word_ratio),]
#[@Meltzer and Holliday_2010]
```


```{r}
# two words
cl_lithic <- JSTOR_2words(multiple_archives, "climate", "lithic")
cl_lithic$plot
```

```{r}
# correlation of two words
co_cl_lithic <- JSTOR_2wordcor(multiple_archives, "climate", "lithic")
co_cl_lithic$plot
```

```{r}
PCA_climate <- JSTOR_clusterbywords(nouns, "climate", f = 0.005)
```

```{r}
climate_nouns <- JSTOR_dtmofnouns(multiple_archives, word = "climate", sparse = 1, POStag = TRUE)
climate_freqwords <- JSTOR_freqwords(multiple_archives, climate_nouns, custom_stopwords, n = 5)
```

```{r}
cl_lithic_nouns <- JSTOR_dtmofnouns(multiple_archives, word = c("climate","lithic"), sparse = 1, POStag = TRUE)
cl_lithic_freqwords <- JSTOR_freqwords(multiple_archives, ev_lithic_nouns, custom_stopwords, n = 5)

```




##Discussion


